### 2023-08-23 appendix.tex
section

Let us recall the undecidable \cite{araki1976PN} decision problem of {\em zero-reachability} in reset-VASS, which consists in, given a
reset-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$,
deciding whether $\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$.
We describe therein how to adjust Theorem~5.5 from \cite{peterson1981petri} reducing the problem to {\sc $t$-liveness}. \\

@@

The new reset-VASS is constructed by adding four new vector coordinate
and
$|V_1|+4$ new transitions for every control-state.

@@

Now we need to see if that vector is zero.
% Now we need to see if that marking is zero.
\alain{structurer la preuve pour la rendre lisible, nommer les objets, faire des paragraphes,...}
We introduce two new additional vector coordinate and $d$ new transitions which have
$-1$ on the $d$-th vector coordinate and $+1$ on this penultimate coordinate.

@@

If $q(\textbf{0})$ is reachable, then these $d$ new transitions are not live. Everything is dead if $s$ fires in $q(\textbf{0})$.

@@

Conversely, if $V_2$ is not live, then a vector is reachable in which the last two coordinate are equal to $0$ and there is no reachable vector in which either is equal to at least one.
% Conversely, if $C_2$ is not live, then a marking $\mu$ must be reachable in which  $\mu(r_2) = 0$ and there is no reachable state in which $r_2$ has a token (in particular, since we do not allow token removal from $r_2$, the marking $\mu$ must be reached in a sequence of transitions that do not place any token in $r_2$.).
If it is not possible to have a strictly positive integer in one of the last two coordinates, then the transitions are not live, and the
$d$-dimensional subset of the current vector must be zero.
% If $r_2$ has no token and cannot get any, then the transitions $s_p$ are not live, and the markings of $p$ for $p \in P_1$ must be zero. 
% Thus if $C_2$ is not live then a marking is reachable in which the marking of each $p$ in $P_1$ is zero. 
Thus if $V_2$ is not live then 
$q(\textbf{0})$ is reachable.
\end{proof}

>>>>

Let us recall the undecidable \cite{araki1976PN} decision problem of {\em zero-reachability} in reset-VASS, which consists in, given a
reset-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$,
deciding whether $\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$.
We describe therein how to adjust Theorem~5.5 from \cite{peterson1981petri} reducing the {\em zero-reachability} problem to {\sc $t$-liveness}. \\

@@

{\bf construction of $V_2$}
The new reset-VASS is constructed by adding four new vector coordinate
and
$|V_1|+4$ new transitions for every control-state.

@@

Now we need to see if that vector is zero.
% Now we need to see if that marking is zero.
\alain{structurer la preuve pour la rendre lisible, nommer les objets, faire des paragraphes,...}
We introduce two new additional vector coordinate and $d$ new transitions which have
$-1$ on the $d$-th vector coordinate and $+1$ on this penultimate coordinate. \\

@@

Let us now prove that $V_2$ is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$.

{\bf Suppose that $q(\textbf{0})$ is reachable from $q_0(\textbf{u})$} in V1 or V2 ????\\
Then these \alain{vague} $d$ new transitions are not live. Everything \alain{vague} is dead if $s$ fires in $q(\textbf{0})$.

@@

{\bf Suppose that $V_2$ is not live and prove that 
$q(\textbf{0})$ is reachable in V12 ???}\\

if $V_2$ is not live, then a vector \alain{vague} is reachable in which the last two coordinate are equal to $0$ and there is no reachable vector in which either is equal to at least one.
% Conversely, if $C_2$ is not live, then a marking $\mu$ must be reachable in which  $\mu(r_2) = 0$ and there is no reachable state in which $r_2$ has a token (in particular, since we do not allow token removal from $r_2$, the marking $\mu$ must be reached in a sequence of transitions that do not place any token in $r_2$.).
If it is not possible to have a strictly positive integer in one of the last two coordinates, then the transitions \alain{vague} are not live, and the
$d$-dimensional subset of the current vector must be zero.
% If $r_2$ has no token and cannot get any, then the transitions $s_p$ are not live, and the markings of $p$ for $p \in P_1$ must be zero. 
% Thus if $C_2$ is not live then a marking is reachable in which the marking of each $p$ in $P_1$ is zero. 
Thus if $V_2$ is not live then 
$q(\textbf{0})$ is reachable.
\end{proof}
